\textbf{ Spectrophotometric parallaxes with linear models:\\ Accurate distances for luminous red-giant stars }

### 2018-10-13 paper/sp.tex
notes to self
new plot
quality cuts

% To-do items
% -----------
% - Coryn's point that we should carefully explain how our model is geometric.
% - check with WISE experts that we have the correct WISE photometry
% - write words about other linear models we have made or could make, probably in the discusssion.
% - are we citing all the proper DR2 papers we need to cite?
% - HWR: Footnote to explain the use of the word ``feature'' for astronomers.
% - HWR: Figures 1 and 2 need to be combined to directly compare Parent and Training.
% - HWR: Figure 3: Note that the y-axis is positive-definite!
% - HWR: Figure 7: Caption needs to say what arrows represent.
% - Make the comparison with Cannon as a function of L1 strength and maybe look at correlation coefficients between parameter vectors.
% - Get model running on ASPCAP outputs and compare in Discussion.
% - Make sure we incorporate / respond to Ness comments from Aug 13 email.
% - Thank APOGEE telecon and add paragraph about AGB stars and the color-magnitude diagram in the discussion.
% - Describe how we ran The Cannon; discussion of how we compare to The Cannon.
% - Cite and describe Eilers et al.

@@

For training, we need A and B Training Sets.
We define the Training Set stars to be Parent-Sample stars that also
have a measured \gaia\ parallax.
The Training-Set stars, in addition to meeting all Parent-Sample cuts,
also must meet ACE WHAT ADDITIONAL CUTS to ensure that the parallax
measurements are good.
These cuts leave 28226 stars total in the Training Sets.
But---as we have emphasized above---we do not cut ever on parallax or
parallax error or their ratio. For this reason, most of the training set
do not have significantly measured parallaxes and more than 2~percent even have
negative parallaxes!
But we will perform our training such that it will be unbiased in these
circumstances.
Indeed it would be necessarily biased if ever we did cut on parallax or
parallax signal-to-noise.

@@

>>>>

% To-do items
% -----------
% - Coryn's point that we should carefully explain how our model is geometric.
% - check with WISE experts that we have the correct WISE photometry
% - write words about other linear models we have made or could make, probably in the discusssion.
% - are we citing all the proper DR2 papers we need to cite?
% - HWR: Footnote to explain the use of the word ``feature'' for astronomers.
% - HWR: Figures 1 and 2 need to be combined to directly compare Parent and Training.
% - HWR: Figure 3: Note that the y-axis is positive-definite!
% - HWR: Figure 7: Caption needs to say what arrows represent.
% - Make the comparison with Cannon as a function of L1 strength and maybe look at correlation coefficients between parameter vectors.
% - Get model running on ASPCAP outputs and compare in Discussion.
% - Make sure we incorporate / respond to Ness comments from Aug 13 email.
% - Thank APOGEE telecon and add paragraph about AGB stars and the color-magnitude diagram in the discussion.
% - Describe how we ran The Cannon; discussion of how we compare to The Cannon.
% - Cite and describe Eilers et al.
% - comment on parallax offset being a function of position and color
% - remove Cannon plot for the moment
% - comment on new plot of new precision on parallax compared to Gaia's precision

@@

For training, we need A and B Training Sets.
We define the Training Set stars to be Parent-Sample stars that also
have a measured \gaia\ parallax.
The Training-Set stars, in addition to meeting all Parent-Sample cuts,
also must meet $\sigma_{\varpi^{(\rm a)}} < 0.1$, it must be observed by \gaia\ for more than $8$ individual times, i.e. \code{visibility_periods_used}~$\geq~8$, as well as meet the additional quality criterion $\code{astrometric_chi2_al}/\sqrt{\code{astrometric_n_good_obs_al}-5} \leq 35$, which eliminates detections that are not consistent with a single PSF \citep[see][]{calj}, to ensure that the parallax
measurements are good.
These cuts leave 28226 stars total in the Training Sets.
But---as we have emphasized above---we do not cut ever on parallax or
parallax error or their ratio. For this reason, most of the training set
do not have significantly measured parallaxes and more than 2~percent even have
negative parallaxes!
But we will perform our training such that it will be unbiased in these
circumstances.
Indeed it would be necessarily biased if ever we did cut on parallax or
parallax signal-to-noise.

@@

% HOGG: NEW FIGURE -- put some words in the text about the figure. 
\begin{figure}
\centering
\includegraphics[width=\textwidth]{./precision.pdf}
\caption{some smart words :) \label{fig:precision}}
\end{figure}
